Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-04-11 ms.tex
continue updating

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
\title[Short Title]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits}

@@

\section{INTRODUCTION}
\editorial{The introduction is now much longer because I talked about the cons to the different cluster mass recovery methods. I don't much care for really long introductions, so if there is anything that could by cut to shorten it, I would be ok.}
Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point. The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the number and masses of galaxy clusters throughout the universe. However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem. Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass \citeeg{Sehgal2011,Plank2014, Bocquet2015}.

@@

One could use various simulations to attempt to calibrate this observable--mass relation \citeeg{Vanderlinde2010, Sehgal2011}. However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments. While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required to the point where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.

@@

The statistical method of determining galaxy cluster mass relies not on direct measurements of individual clusters but the calibration of observables for the entire sample which correlate with cluster mass. One example is the spatial clustering of the galaxy clusters themselves. See \cite{Weinberg2013} for a comprehensive review. In practice, it will be a combination of the three methods touched on that will provide the most reliable determination of cluster masses.

@@

While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}). The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

@@

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a 398.49 \degsq\ mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.

The catalog information, used in this study, is broken into two large portions. The ``truth'' files contain the characteristics of each individual galaxies, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others. The ``halo'' files contain information for individual halos, to which many individual galaxies may belong. This includes five estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others. However, the catalogs do not include information for emission lines. We supplement the catalogs by generating this information; the process is described in Section~\ref{sec: oii luminosity}.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters. \editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts. Might be helpful, might not matter.}

@@

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively. For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity. Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.

@@

In this work we consider two separate observing strategies, targeted and survey-like. The targeted observations use ``direct'' observations where each cluster is targeted individual, and every cluster member galaxy is assumed to be observed. The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, for comparison we also include a set of targeted observations with ``perfect'' knowledge. ``Perfect'' observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the recovered cluster properties are still calculated. These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
 In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. This is not meant to be an exhaustive study of the different methods used to recover these parameters. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with observational studies.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters.

@@

The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value. The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$. The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.

@@

\subsubsection{Machine Learning Based}\label{sec:machine learning method}
The estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation. Ensemble methods come in two general flavors. Averaging methods average (hence the name) the estimators to produce a single prediction. Boosting estimators build estimates sequentially by attempting to address poor performing estimators in each previous step, hence ``boosting'' the predictive power.

Here we use an averaging ensemble learning method known as a forest of randomized decision trees often shorten to just random forest (RF). Decision trees can be visualized a flow chart where forks are the branches of the tree. The path along the tree is decided by the values of the feature at each branch. RF estimators use a random subset of the training set at each fork to decide which path should be followed. The final prediction is then the average of all the trees. We use RF regression methods as implemented in {\tt Scikit-Learn} \citep{Pedregosa2012}.

@@

\subsection{Recovery of Cluster Members}
As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or targeted observations. Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

For the clusters recovered as a function of redshift, there are two effects at work. The decrease in recovery fraction with increasing redshift is a magnitude effect. We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold. The second key feature is the strong decline in clusters recovered from survey observations. This is due to gaps in the VIRUS IFU. The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction. As the total filling factor of the survey increases the two lines will converge.

@@

\subsection{Mass estimates}
% \begin{table*}
% \centering
% \caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions. See the text for discussion about the MAE and RMSE. Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass. See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
% \begin{tabular}{cccccccc}
% 	%\hline
% 	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
% 	\cline{3-5} \cline{6-8}
% 	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
% 	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
% 	\hline
% 	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
% 	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
% 	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
% 	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
% 	\hline
% 	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
% 	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
% 	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
% 	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
% 	\hline
% \end{tabular}
% \label{tbl:mass comparisons}
% \end{table*}

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison} 
\end{figure*}

In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations. We report on three methods, the power law based approach (Eq. \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider observations with perfect knowledge, targeted observations and survey observations.

Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias 
\begin{equation}
\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).
\end{equation}
where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
\begin{equation}
	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

We begin with the perfect knowledge observations. These observations are of the same clusters as the targeted observations but without any observational limits. The cluster masses predicted by Equation \ref{eq:power law} gives the following results. Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex. The scatter in recovered masses can be attributed to both physical and numerical effects. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs. We could do something similar and have a similar discussion, but I'm not sure it is worth it. Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO. We should also talk about how often the true mass lies within the error bars. Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}

@@

In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true (M) cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). For reference we also show the median masses recovered with perfect knowledge as a solid orange line. The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M)/M
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.

@@

\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass. This table shows the bias in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}

@@

@@

We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}. It should serve as a type of look up table for future cluster observations with HETDEX. The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass. The three horizontal sections represent perfect, targeted and survey observations respectively. So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm{0.00}$ dex.

 A few caveats apply to the numbers given in Table \ref{tbl:mass bias}. While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters. On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons. There are very few, if any, clusters detected with survey observations below $10^{12}$ \msol. Missing corrections above $10^{12}$ \msol\ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.

@@

Cluster masses are assigned using the ML methods (see Section \ref{sec:machine learning method}) using two different training sets. We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters.

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig: mill buzz comparison} 
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
\title[Galaxy Clusters with HETDEX]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology}

@@

\section{INTRODUCTION}
Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point. The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the number and masses of galaxy clusters throughout the universe. However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem. Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass \citeeg{Sehgal2011,Plank2014, Bocquet2015}.

@@

One could use various simulations to attempt to calibrate this observable--mass relation \citeeg{Vanderlinde2010, Sehgal2011}. However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments. While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.

@@

The statistical method of determining galaxy cluster mass relies not on direct measurements of individual clusters but the calibration of observables for the entire sample which correlate with cluster mass. One example is the spatial clustering of the galaxy clusters themselves \citeeg{Baxter2016}. See \cite{Weinberg2013} for a comprehensive review. In practice, it will be a combination of the three methods touched on that will provide the most reliable determination of cluster masses.

@@

While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$. The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

@@

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.

The catalog information, used in this study, is broken into two large portions. The ``truth'' files contain the characteristics of each individual galaxy, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others. The ``halo'' files contain information for individual halos, to which many individual galaxies may belong. This includes five estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others. However, the catalogs do not include information for emission lines. We supplement the catalogs by generating this information; the process is described in Section~\ref{sec: oii luminosity}.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters. \editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts. Might be helpful, might not matter.}

@@

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively. For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity. Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.

@@

In this work we consider two separate observing strategies, targeted and survey-like. The targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, for comparison we also include a set of targeted observations with ``perfect'' knowledge. Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the recovered cluster properties are still calculated. These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
 In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. This is not meant to be an exhaustive study of the different methods used to recover these parameters. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters \citeeg{Boada2016a}.

@@

The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value. The slices shown by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$. The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.

@@

\subsubsection{Machine Learning Based}\label{sec:machine learning method}
The cluster mass estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation. Ensemble methods come in two general flavors. Averaging methods average (hence the name) the estimators to produce a single prediction. Boosting estimators build estimates sequentially by attempting to address poor performing estimators in each previous step, hence ``boosting'' the predictive power.

Here we use an averaging ensemble learning method known as a forest of randomized decision trees often shorten to just random forest (RF). Decision trees can be visualized a flow chart where forks are the branches of the tree. The path along the tree is decided by the values of the feature at each branch. RF estimators use a random subset of the training set at each fork to decide which path should be followed. The final prediction is then the average of all the trees. We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.

@@

\subsection{Recovery of Cluster Members}
As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or targeted observations. Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this Figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

For the clusters recovered as a function of redshift (left panel of Figure \ref{fig: recovery}), there are two effects at work. The decrease in recovery fraction with increasing redshift is a magnitude effect. We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold. The second key feature is the strong decline in clusters recovered from survey observations. This is due to gaps in the VIRUS IFU. The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction. As the total filling factor of the survey increases the two lines will converge.

@@

\subsection{Mass estimates}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison} 
\end{figure*}

In this section we discuss the how accurately we recover the true cluster mass from a set of observations. We report on three methods, the power law based approach (Eq. \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider observations with perfect knowledge, targeted observations and survey observations.

Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
\begin{equation}
\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).
\end{equation}
where $y$ are the true values and $\hat{y}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
\begin{equation}
	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

We begin with the perfect knowledge observations. These observations are of the same clusters as the targeted observations but without any observational limits. The cluster masses predicted by Equation \ref{eq:power law} gives the following results. Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex. The scatter in recovered masses can be attributed to both physical and numerical effects. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

% \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs. We could do something similar and have a similar discussion, but I'm not sure it is worth it. Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO. We should also talk about how often the true mass lies within the error bars. Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}

@@

In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true ($M_{200c}$) cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). For reference we also show the median masses recovered with perfect knowledge as a solid orange line. The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M_{200c})/M_{200c}
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass.

@@

\caption{Mean bias ($M_{pred}$ - $M_{200c}$) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}

@@

		&& \multic{8}{Bins -- Log $M_{pred}$} \\

@@

We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}. It should serve as a type of look up table for future cluster observations with HETDEX. The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass. The three horizontal sections represent perfect, targeted and survey observations respectively. So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm{0.00}$ dex.

 A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}. While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters. On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons. There are very few, if any, clusters detected with survey observations below $10^{12}$ \msol. Missing corrections above $10^{12}$ \msol\ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.

@@

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
	\caption{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line). The shaded areas show the 68\% scatter around the median. The solid black line shows the 1:1 relation.The solid black line shows the 1:1 relation. \emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison} 
\end{figure}
